---
title: "cytomarker Run Report"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  marker_selection: ""
  heatmap: ""
  umap: ""
  metric: ""
  config: ""
  tmpdir: ""
  overall: ""
header-includes:
  - \usepackage{fontawesome5}
---

<style>
.main-container {
    max-width: 940px;
    margin-right: auto;
}
</style>

Below are the results of your cytomarker antibody panel design run.

```{r message=FALSE, echo=F}
knitr::opts_knit$set(root.dir = params$tmpdir)
# library(tidyverse)
library(DT)
library(yaml)
library(shiny)
library(printr)
library(reactable)
library(plotly)
library(htmltools)
library(fontawesome)
library(emojifont)
```


```{r, echo=FALSE}
htmltools::img(src = "cytomarker-logo.png", 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding-top: 20px; padding-right:40px; width: 185px;')
```

## Selected markers {.tabset}

### Marker list vector

You selected the following markers to be included in your antibody panel. It can be copied directly as a R-compatible vector. 

```{r message=FALSE, echo=F, comment=NA}
with_quotes <- paste0("'", names(params$marker_selection), "'")
first_genes <- paste0(utils::head(with_quotes, n = length(with_quotes) - 1), collapse = " ", sep = ",")
all_genes <- paste0("c(", first_genes, " ", tail(with_quotes, n = 1), ")")
cat(all_genes)
```

### Marker/Cell-type table

```{r message=FALSE, echo=F, comment=NA}
reactable(data.frame(Marker = names(params$marker_selection),
                     Annotation = params$marker_selection),
          rownames = F,
           searchable = TRUE,
                filterable = TRUE)
```


## Heatmaps  {.tabset}

### Marker-marker correlation

```{r echo=F, warning=F, fig.width=9}
params$heatmap$correlation
```

### Marker Expression

```{r echo=F, warning=F, fig.width=9}
params$heatmap$expression
```

### Marker Z-score

```{r echo=F, warning=F, fig.width=9}
params$heatmap$z_score
```

## UMAPs {.tabset}

### All Markers

```{r echo = F, fig.width=8, fig.height=5, warning=F, message=F}
params$umap$all

```

### Selected Marker Panel

```{r echo = F, fig.width=8, fig.height=5, warning=F, message=F}
params$umap$top

```

## Overall Score

```{r echo=F, warning=F, fig.width=3.5, fig.height=3.5}
overall_frame <- data.frame(x = 2, y = 2.5, h = 4.25, w = 4.25,
                            value = params$overall$score[1],
                            info = "Accuracy score,",
                            info_2 = paste("n = ", params$overall$counts[1]),
                            icon = fontawesome(search_fontawesome("chart"))[1],
                            font_family = "fontawesome-webfont",
                            color = 1)

ggplot(overall_frame, aes(x, y, height = h, width = w, label = info)) +
  ## Create the tiles using the `color` column
  geom_tile(aes(fill = color)) +
  ## Add the numeric values as text in `value` column
  geom_text(color = "white", fontface = "bold", size = 25,
            aes(label = value, x = x - 1.7, y = y + 1.25), hjust = 0) +
  ## Add the labels for each box stored in the `info` column
  geom_text(color = "white", fontface = "bold", size = 15,
            aes(label = info, x = x - 1.7, y = y - 1), hjust = 0) +
  geom_text(color = "white", fontface = "bold", size = 15,
            aes(label = info_2, x = x - 1.7, y = y - 1.45), hjust = 0) +
  coord_fixed() +
  ## Use `geom_text()` to add the icons by specifying the unicode symbol.
  geom_text(size = 40, aes(label = icon, family = font_family,
                           x = x + 1, y = y + 0.2), alpha = 0.25) +
  theme_void() +
  guides(fill = FALSE)

```

## Detailed Metrics {.tabset}


### Distribution

```{r echo=F, warning=F, fig.width=10}
params$metric$plot
```


### Summary Table

```{r echo=F, warning=F, fig.width=10}
params$metric$table |> 
  datatable(options = list(autoWidth = FALSE))
```


## Config

Below is the configuration used during your run:

```{r echo = F,message=F}
params$config |> 
  datatable(options = list(autoWidth = FALSE))
```
